---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE, message = FALSE
)
```

# BOP2-FE

<!-- badges: start -->
<!-- badges: end -->

The primary purpose of an oncology single-arm trial is to evaluate the effectiveness
of anticancer agents and make a go / no-go decision while maintaining patient safety.
This R-package implements a flexible Bayesian optimal phase II design with futility and efficacy
stopping boundaries for single-arm clinical trials, named the BOP2-FE design, proposed by Xu et al (under review). The
proposed BOP2-FE design allows for early stopping of efficacy when the observed
antitumor effect is sufficiently higher than the null hypothesis value in the interim
looks and retains the benefits of the original BOP2 design, such as explicitly controlling the type I error rate while maximizing power, accommodating different types
of endpoint, flexible number of interim looks, and stopping boundaries calculated
before the start of the trial. The package handles multiple endpoints including binary, nested, co-primary and joint efficacy and toxicity. 

## Installation

You can install the development version of BOP2FE from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("belayb/BOP2FE")
```

## Example

This is a basic example which shows you how to use BOP2FE:

```{r example}
library(BOP2FE)
## basic example code
```

### Binary endpoint 

```{r binary}
BOP2FE_binary(H0 =0.2, n = c(10,5,5,5,5,5,5), lambda = 0.909, gamma=1, nsim = 10000, seed = 1234)
```

### Nested endpoint 

```{r nested}
BOP2FE_nested(CR0 = 0.15, CRPR0 = 0.30, n=c(10,5,5,5,5,5,5), lambda = 0.95, gamma=1, seed = 123)
```


### Co-primary endpoint 

```{r coprimary}
BOP2FE_coprimary(H0 = c(0.05,0.05,0.15,0.75), n=c(10,5,5,5,5,5,5), lambda = 0.95, gamma=1,seed = 123)
```


### Joint endpoint 

```{r joint}
BOP2FE_jointefftox(H0 = c(0.15, 0.30, 0.15, 0.40), n=c(10,5,5,5,5,5,5), lambda = 0.7, gamma=1, seed = 123)
```

### Optimizing Design Parameters 
The operating characteristics of the BOP2-FE design with futility and efficacy stopping rules depend on the specification of the probability cutoffs for futility and efficacy. To maximize statistical power while controlling the type I error rate at a certain prespecified level, the tuning parameters, (lambda, gamma, eta) when using the power function for the probability cutoffs for efficacy, and (lambda, gamma) when using the O’Brien-Fleming type function for the probability cutoffs for efficacy, should be identified through simulation as follows. 

```{r optimal}
Sim_res <- Optimal_pars_nested(CR0=0.15, CRPR0=0.30, CR1=0.25, CRPR1=0.50, n=c(20,10,10), nsim=1000, t1e=0.1, t2e=0.2, method="power",
                                lambda1=0.85, lambda2=1, grid1=5, gamma1=0.9, gamma2=1.1, grid2=5, eta1=0.9, eta2=1.1, grid3=5)

head(Sim_res)
```

